### 2019-01-27 gameth1.tex
Gametheory

Assume $\sigma^* \in \times_{i \in I}\Delta(S_i)$ is a Nash equilibrium. And assume that for a player $i$, $\sigma_i^*$ assigns a positive probability to the pure strategy $s_j$ which is strictly dominated by the strategy $\sigma_i$. Then 
\begin{align*}
&\exists\ \alpha_1, \dots, \alpha_{|S_i|}: \alpha_k \in [0, 1]\ \forall\ k, \sum_{k=1}^{|S_i|}\alpha_k = 1\text{ and }\\
 u_i(\sigma^*_i, \sigma^*_{-i}) = &\alpha_1 u_1(s_1, \sigma^*_{-i}) + \dots + \alpha_j u_i(s_j, \sigma^*_{-i}) + \dots + \alpha_{|S_i|}u_i(s_{|S_i|}, \sigma^*_{-i}),\ \  \alpha_j > 0
\end{align*}
Since $\sigma_i$ strictly dominates $s_j$ then
\begin{align*}
&\exists\ \beta_1, \dots, \beta_{|S_i|}:\beta_k \in [0, 1]\ \forall\ k,\ \sum_{k=1}^{|S_i|}\beta_k = 1\text{ and }
\forall\ \sigma_{-i} \in \times_{l \in I\setminus \left\{i\right\}}\Delta(S_l)\\
u(s_j, \sigma_{-i}) < &u(\sigma_i, \sigma_{-i}) = \beta_1 u_i(s_1, \sigma_{-i}) + \dots + \beta_j u_i(s_j, \sigma_{-i}) + \dots + \beta_{|S_i|}u_i(s_{|S_i|}, \sigma_{-i})
\end{align*}
But then
\begin{align*}
&u_i(\sigma_i^*, \sigma^*_{-i}) < \alpha_1u_1(s_1, \sigma^*_{-i}) + \dots + \alpha_j \left(\sum_{k=1}^{|S_i|}\beta_k u_i(s_k, \sigma^*_{-i})\right) + \dots + \alpha_{|S_i|}u_i(s_{|S_i|}, \sigma^*_{-i}) = \\
&= (\alpha_1 + \alpha_j\beta_1)u_i(s_1, \sigma^*_{-i}) + \dots + (\alpha_j + \alpha_j\beta_j)u_i(s_1, \sigma^*_{-i}) + \dots + (\alpha_{|S_i|} + \alpha_{|S_i|}\beta_{|S_i|})u_i(s_{|S_i|}, \sigma^*_{-i}) = \\
&=u(\hat{\sigma_i}, \sigma^*_{-i})
\end{align*}
Since $\exists\ t \in 1, \dots, |S_i|: \beta_{t} > 0\ \to \alpha_t + \alpha_j \beta_t \neq \alpha_t$ hence there exists another strategy $\hat{\sigma_i} \neq \sigma^*_i$ which gives strictly greater payoff than $\sigma^*_i$ hence $\sigma^*$ is not a Nash equilibrium, contradiction. This contradiction shows that indeed $\alpha_j = 0$ i.e. the euilibrium strategy must assign $0$ probability to the strictly dominated strategy.
\end{document}

>>>>

Assume $\sigma^* \in \times_{i \in I}\Delta(S_i)$ is a Nash equilibrium. And assume that for a player $i$, $\sigma_i^*$ assigns a positive probability to the pure strategy $s_j$ which is strictly dominated by the strategy $\sigma_i$. Then 
\begin{align*}
&\exists\ \alpha_1, \dots, \alpha_{|S_i|}: \alpha_k \in [0, 1]\ \forall\ k, \sum_{k=1}^{|S_i|}\alpha_k = 1\text{ and }\\
 u_i(\sigma^*_i, \sigma^*_{-i}) = &\alpha_1 u_1(s_1, \sigma^*_{-i}) + \dots + \alpha_j u_i(s_j, \sigma^*_{-i}) + \dots + \alpha_{|S_i|}u_i(s_{|S_i|}, \sigma^*_{-i}),\ \  \alpha_j > 0
\end{align*}
Since $\sigma_i$ strictly dominates $s_j$ then
\begin{align*}
&\exists\ \beta_1, \dots, \beta_{|S_i|}:\beta_k \in [0, 1]\ \forall\ k,\ \sum_{k=1}^{|S_i|}\beta_k = 1\text{ and }
\forall\ \sigma_{-i} \in \times_{l \in I\setminus \left\{i\right\}}\Delta(S_l)\\
u(s_j, \sigma_{-i}) < &u(\sigma_i, \sigma_{-i}) = \beta_1 u_i(s_1, \sigma_{-i}) + \dots + \beta_j u_i(s_j, \sigma_{-i}) + \dots + \beta_{|S_i|}u_i(s_{|S_i|}, \sigma_{-i})
\end{align*}
But then
\begin{align*}
&u_i(\sigma_i^*, \sigma^*_{-i}) < \alpha_1u_1(s_1, \sigma^*_{-i}) + \dots + \alpha_j \left(\sum_{k=1}^{|S_i|}\beta_k u_i(s_k, \sigma^*_{-i})\right) + \dots + \alpha_{|S_i|}u_i(s_{|S_i|}, \sigma^*_{-i}) = \\
&= (\alpha_1 + \alpha_j\beta_1)u_i(s_1, \sigma^*_{-i}) + \dots + (\alpha_j + \alpha_j\beta_j)u_i(s_1, \sigma^*_{-i}) + \dots + (\alpha_{|S_i|} + \alpha_{|S_i|}\beta_{|S_i|})u_i(s_{|S_i|}, \sigma^*_{-i}) = \\
&=u(\hat{\sigma_i}, \sigma^*_{-i})
\end{align*}
Since $\exists\ t \in 1, \dots, |S_i|: \beta_{t} > 0\ \to \alpha_t + \alpha_j \beta_t \neq \alpha_t$ hence there exists another strategy $\hat{\sigma_i} \neq \sigma^*_i$ which gives strictly greater payoff than $\sigma^*_i$ hence $\sigma^*$ is not a Nash equilibrium, contradiction. This contradiction shows that indeed $\alpha_j = 0$ i.e. the euilibrium strategy must assign $0$ probability to the strictly dominated strategy.
\section*{Problem 3}
There are $n < +\infty$ firms in an industry. Each can try to convince Congress
to give the industry a subsidy. Let $h_i$ denote the hours of effort put by
some industry $i \in \left\{1,\dots , n\right\}$. Let $c(h_i) = w_ih_i^2$, with $w_i > 0$, be the cost of
this effort to firm $i$. For each profile of efforts $(h_1, \dots , h_n) \in \mathbb{R}^n_+$, the value
of the subsidy that gets approved equals

\begin{align*}
\alpha \sum_{i \in \left\{1, \dots, n\right\}} h_i + \beta \left(\prod_{i \in \left\{1, \dots, n\right\}} h_i\right)
\end{align*}
where $\alpha, \beta \ge 0$. The approved subsidy is shared equally among the firms in
the industry. Suppose that all firms choose the effort level simultaneously.
Show that each firm has a strictly dominant strategy if and only if $\beta = 0$.
What is firm $i$’s strictly dominant strategy when this is so?

Each firm's payoff function is:
\begin{align*}
u_i(h_1, \dots, h_i, \dots, h_n) = \alpha \cdot \frac{h_1 + \dots h_i + \dots + h_n}{n} + \beta h_1\times\dots\times h_i \times \dots\times h_n - w_ih_i^2
\end{align*}

hence to find a strictly dominant strategy one need to find $h_i^*$:
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \forall\ h_{-i}, \forall\ h_i
\end{align*}
Suppose $\beta = 0$ then 
\begin{align*}
u_i(h_i, h_{-i}) = \alpha\frac{h_i}{n} + \alpha\frac{h_1 + \dots+h_{i-1}+h_{i+1}+\dots+h_n}{n} - w_ih_i^2
\end{align*}
it is a quandratic function in $h_i$ and regardless of what $h_j\ \forall\ j \in\left\{1, \dots, n\right\}\setminus \left\{i\right\}$ is it attains maximum at $h_i = \frac{\alpha}{2nw_i}$. Thus, strategy $h_i = \frac{\alpha}{2nw_i}$ is a strictly dominant strategy for each firm in case $\beta = 0$. Now assume conversly that each firm has a strictly dominant strategy $h_i^*$. Then 
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \  \forall\ h_i, h_{-i}
\end{align*}
Suppose by contradiction that $\beta > 0$. Let us denote $\prod_{k \in \left\{1, \dots, n\right\}\setminus\left\{i\right\}}h_k$ as $H_{-i}$ then if for some $h_{-i}$ - profile of strategies of other players
\begin{align*}
u_i(h_i^*, h_{-i}) > u_i(h_i, h_{-i})\ \forall\ h_i \neq h_{i}^*
\end{align*}
then $h_{i}^*$ is the extremum of the payoff function, given $H_{-i}$, i.e.
\begin{align*}
h_i^* = \frac{\alpha}{2nw_i} + \frac{\beta}{2nw_i}H_{-i}
\end{align*}
but now suppose $\forall j = 1, \dots, i-1, i+1, \dots, n$, $\hat{h_j} = \varepsilon^{\frac{1}{n-1}}h_j$ for some positive $\varepsilon$. Then
\begin{align*}
\exists\ \hat{h_i} = \frac{\alpha}{2nw_i} + \frac{\varepsilon \beta}{2nw_i}H_{-i} \neq h^*_i: u_i(\hat{h_i}, \hat{h_{-i}}) \ge u_i(h_i^*, \hat{h_{-i}})
\end{align*}
Because the value of the function at its maximum is always greater or equal than in any other point. That means that $h_i^*$ is not a strictly dominant strategy. This contradiction shows that $\beta = 0$. Q.E.D.
\section*{Problem 4}
Prove the following statement
In a finite simultaneous move game representable in normal form,
\begin{align*}
\Gamma =
(I, \times_{i \in I}S_i,(u_i)_{i\in I})
\end{align*}
if a single profile of pure strategies survives the process of iterated deletion
of strictly dominated strategies, then this profile must be the unique Nash
equilibrium of the game

\end{document}
